
---
title: "Gambling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggthemes)
library(ggplot2)
library(tidyverse)
library(pracma)  # imports Mode function
```

## Load the data

```{r}
gambling <- read_tsv("gambling_data.txt")
gambling <- gambling %>%
  filter(!is.na(TrialType)) 

gambling$TrialType <- as_factor(gambling$TrialType)

# Divide into blocks

blockId <- sort(rep(1:4, 8))

gambling <- gambling %>% 
  group_by(HCPID, RunNumber) %>%
  mutate(BlockId = blockId)

bg <- gambling %>%
  group_by(BlockId, HCPID, RunNumber) %>%
  summarise(BlockType = Mode(TrialType))

gambling <- inner_join(gambling, bg)
```


```{r}
ggplot(gambling, aes(x=QuestionMark.RT, fill=BlockType)) +
  geom_histogram(binwidth = 50, col="white", alpha=0.5, position = "identity") +
  #facet_wrap(~BlockType) +
  theme_pander()

ggplot(gambling, aes(x=HCPID, y=QuestionMark.RT, col=BlockType))+
  stat_summary(fun.data="mean_se") +
  theme_pander()

same <- gambling %>%
  group_by(HCPID, RunNumber, BlockId, BlockType) %>%
#  filter(ConsecSameResp < 10) %>%
  summarise(MCSR = max(ConsecSameResp))

ggplot(same, aes(x=HCPID, y=MCSR, col=BlockType)) +
  stat_summary(fun.data="mean_se") +
  theme_pander()

ggplot(same, aes(x=BlockType, y=MCSR, col=BlockType))+
  stat_summary(geom = "errorbar", fun.data="mean_se") +
  geom_violin(aes(fill=BlockType), alpha=0.2) +
  theme_pander()

ggplot(same, aes(x=MCSR, col=BlockType))+
  #stat_summary(geom = "errorbar", fun.data="mean_se") +
  geom_density(aes(fill=BlockType), alpha=0.2, position = "identity") +
  theme_pander()
```

# Compute win-stay probabilities

The most meaningful way to analyzed the data is through Win-Stay, Lose-Shift (WSLS) Basically, we calculate the probability of switching response after a Punishment and after a Reward. To compute these metrics, we first need to offset the choices.

```{r}
future_moves <- function(responses) {
  c(responses[2:length(responses)], NA)
}
```

We can now compute future moves for every block. We will remove the the last trials, which is marked as NA by the `future_moves` function (since there is no future at the end of a trial)

```{r}
gambling <- gambling %>%
  group_by(HCPID, RunNumber, BlockId) %>%
  mutate(Response = if_else(is.na(QuestionMark.RESP), 0, QuestionMark.RESP)) %>%
  mutate(CurrentResponse = Response,
         FutureResponse = future_moves(Response),
         RT = QuestionMark.RT) %>%
  #filter(!is.na(FutureResponse)) %>%
  #filter(!is.na(CurrentResponse)) %>%
  mutate(ResponseSwitch = if_else(CurrentResponse == FutureResponse, 0, 1))   %>%
  select(HCPID, RunNumber, BlockId, RT, Response, CurrentResponse, FutureResponse, ResponseSwitch, BlockType, TrialType)
```

Now, elt's examine whether a Response Switch is more likely to occur after a Reward or a Punishment

```{r}
aggregate <- gambling %>%
  group_by(HCPID, 
           #RunNumber, 
           #BlockId, 
           BlockType, 
           TrialType) %>%
  summarise(PSwitch = mean(ResponseSwitch),
            RT = mean(RT)
            )
```

And now, let;'s visualize

```{r}
ggplot(filter(aggregate, 
              TrialType != "Neutral"), 
       aes(x = TrialType, y = PSwitch, col = TrialType)) +
  facet_wrap(~BlockType) +
  geom_point(position = position_jitter(width = 0.1, height = 0.05),
             alpha = 0.1) +
  scale_color_brewer(palette = "Set2") +
  stat_summary(fun.data = "mean_cl_boot", col="black") +

  #geom_boxplot() +
  theme_pander()
         

ggplot(filter(aggregate, 
              TrialType != "Neutral"),
       aes(x = TrialType, y = PSwitch, col = TrialType)) +
  facet_wrap(~BlockType) +
  scale_color_brewer(palette = "Set2") +
  stat_summary(fun.data = "mean_cl_boot", col="black") +

  #geom_boxplot() +
  theme_pander()


ggplot(filter(aggregate, 
              TrialType != "Neutral"),
       aes(x = TrialType, y = RT, col = TrialType)) +
  facet_wrap(~BlockType) +
  scale_color_brewer(palette = "Set2") +
  stat_summary(fun.data = "mean_cl_boot", col="black") +

  #geom_boxplot() +
  theme_pander()

ggplot(filter(aggregate, 
              TrialType != "Neutral"),
       aes(x = HCPID, y = PSwitch, col = TrialType)) +
  facet_wrap(~BlockType) +
  scale_color_brewer(palette = "Set2") +
  stat_summary(fun.data = "mean_cl_boot", geom="point") +

  #geom_boxplot() +
  theme_pander()
```


```{r}
summary(aov(PSwitch ~ (TrialType * BlockType) + Error(HCPID/(TrialType*BlockType)), aggregate)) 
```

Some participants might be always responding with the same key; let's get rid of them

```{r}
totals <- gambling %>%
  group_by(HCPID, 
           RunNumber, 
           BlockId) %>%
  summarise(Tot = length(Response))

fishbait <- gambling %>%
  group_by(HCPID, 
           RunNumber, 
           #BlockId, 
           #BlockType, 
           Response) %>%
  summarise(Percentage = length(Response)/32)

fishbait$Response <- factor(fishbait$Response)

ggplot(fishbait, aes(x=Percentage, fill=Response)) +
  geom_histogram(aes(fill=Response), 
                 col="white", binwidth = 1/32, 
                 alpha=0.5, position="stack") +
  theme_pander()
```


